\begin{thebibliography}{99}

\bibitem{ted:mcgonigal}
  Jane McGonigal, \\
  TED Conversation \\
  \url{http://www.ted.com/conversations/44/we_spend_3_billion_hours_a_wee.html} \\
  2011. \\
  \emph{Retrieved June 2014}

\bibitem{rebroken}
  Jane McGonigal, \\
  \emph{Reality is Broken: Why Games Make Us Better and How They Can Change the World} \\
  Vintage Digital \\
  2011.

\bibitem{wiki:flappy}
  Wikipedia, \\
  \url{http://en.wikipedia.org/wiki/Flappy_bird} \\
  \emph{Retrieved June 2014}

\bibitem{forbes:flappy}
  Ewan Spence, \\
  \url{http://www.forbes.com/sites/ewanspence/2014/02/18/the-vital-and-depressing-lessons-flappy-bird-can-teach-indie-developers/} \\
  Forbes.com \\
  2014. \\
  \emph{Retrieved June 2014}

\bibitem{wiki:minecraft}
  Wikipedia, \\
  \url{http://en.wikipedia.org/wiki/Minecraft} \\
  \emph{Retrieved June 2014}

\bibitem{flesh}
  David Foster Wallace, \\
  \emph{Both Flesh And Not} \\
  Penguin \\
  2012.

\bibitem{dewey}
  John Dewey, \\
  \emph{The School and Society and The Child and the Curriculum (Centennial Publications of the U of C Pr)} \\
  University of Chicago Press \\
  1915.

\bibitem{ackermann}
  Edith Ackermann, \\
  \emph{Piaget’s Constructivism, Papert’s Constructionism: 
What’s the difference?} \\
  \url{http://learning.media.mit.edu/content/publications/EA.Piaget%20_%20Papert.pdf}
  MIT \\
  \emph{Retrieved June 2014}.

\bibitem{convsinst}
  Seymour Papert, \\
  \url{http://papert.org/articles/const_inst/const_inst1.html} \\
  Papert.org \\
  \emph{Retrieved June 2014}.

\bibitem{sitconst}
  Seymour Papert, Idit Harel \\
  \emph{Constructionism} \\
  Ablex Publishing Corporation \\
  1991.

\bibitem{westeroscraft}
  Laura Hudson, \\
  \url{http://www.wired.com/2013/03/westeroscraft-game-thrones-minecraft/all/}
  Wired \\
  \emph{Retrieved June 2014}.

\bibitem{reddit:minecraft}
  Ikarus3426 \\
  \url{http://www.reddit.com/r/Minecraft/comments/dibqq} \\
  Reddit.com self.Minecraft \\
  \emph{Retrieved June 2014}.  

\bibitem{mash}
  Matt Silverman \\
  \url{http://mashable.com/2013/02/13/amazing-minecraft-creations//#_} \\
  Mashable \\
  \emph{Retrieved June 2014}.

\bibitem{local:minecraft}
  Oliver Gee \\
  \url{http://www.thelocal.se/20130109/45514} \\
  The Local \\
  \emph{Retrieved June 2014}.

\bibitem{neural}
  Shah C, Erhard K, Ortheil HJ, Kaza E, Kessler C, Lotze M. \\
  \emph{Neural correlates of creative writing: an fMRI study.} \\
  University of Greifswald \\
  2011.

\bibitem{reinforcement}
  Richard S. Sutton, Andrew G. Barto \\
  \emph{Reinforcement Learning: An Introduction } \\
  The MIT Press \\

\bibitem{drive}
  Daniel H. Pink \\
  \emph{Drive: The Surprising Truth About What Motivates Us} \\
  Canongate Books \\
  2010.

\bibitem{krznaric}
  Roman Krznaric \\
  \emph{How to Find Fulfilling Work} \\
  Macmillan \\
  2012.

\bibitem{joywork}
  Nick Isles \\
  \url{http://twfold.theworkfoundation.com/assets/docs/publications/145_Joy_of_Work.pdf} \\
  The Work Foundation \\
  \emph{PDF, retrieved June 2014}.

\bibitem{zunshine}
  Lisa Zunshine \\
  \emph{Why We Read Fiction: Theory of Mind and the Novel (Theory and Interpretation of Narrative)} \\
  Ohio State University Press \\
  2012.

\bibitem{ingulfson}
  Eileen Ingulfson \\
  Personal e-mail correspondence \\
  March 2014.

\bibitem{wiki:waterfall}
  Wikipedia, \\
  \url{http://en.wikipedia.org/wiki/Waterfall_model} \\
  \emph{Retrieved June 2014}

\bibitem{leffingwell}
  Dean Leffingwell \\
  \emph{Scaling Software Agility: Best
Practices for Large Enterprises} \\
  Addison-Wesley Professional \\
  2007.

\bibitem{dn:bjorklund}
  Maria Sunden Jelmini \\
  \emph{Tidigare betyg ska lyfta skolan} \\
  \url{http://www.svd.se/nyheter/inrikes/jan-bjorklund-vi-behover-tidigare-betyg_3279172.svd} \\
  Article at SVD.se \\
  2014.

\bibitem{pedmag}
  Hans-Åke Scherp \\
  \emph{
Mer kontroll löser inte problemen} \\
  \url{http://www.lararnasnyheter.se/pedagogiska-magasinet/2014/02/27/mer-kontroll-loser-inte-problemen} \\
  Pedagogiska Magasinet \\
  2014.

\bibitem{debate}
  \emph{Are video games a waste of time?} \\
  \url{http://www.debate.org/opinions/are-video-games-a-waste-of-time} \\
  Debate.org \\
  \emph{Retrieved June 2014}.

\bibitem{reddit:waste}
  Reddit self.changemyview \\
  \url{http://www.reddit.com/r/changemyview/comments/1ye5w2/i_think_that_playing_video_games_is_a_waste_of/} \\
  \emph{Retrieved June 2014}.

\end{thebibliography}
