\documentclass[a4paper]{report}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{graphicx}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=maroon,
            pdfborder={0 0 0}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

\setcounter{secnumdepth}{1}
\setcounter{tocdepth}{1}

\title{Hacking Education with Virtual Microworlds}
\author{Pascal Chatterjee}

\begin{document}

\maketitle

\begin{abstract}
Contrary to popular belief, the scientists working in their laboratories are not the members of society who learn the most in their daily lives. The members of society who do \textit{by far} the most learning in their daily lives are children. 

Children tend to walk by the age of 18 months; they can express themselves in the extremely complex system known as natural language by the age of two years; and they have developed a theory of mind after spending a mere four years in the world. And they manage all of this before entering formal education.

The progress of even the hardest working university student pales in comparison. This is not just due to the difference in age between adults and children. It also has to do with the environment in which we learn.

Microworlds are environments in which adult minds can \textbf{construct} knowledge in a similar way to children. This paper explains the ideas behind microworlds, describes two implementations of them, and discusses whether they worked and if they will ever be a feature of mainstream curricula. 

The microworld created for this paper, \textit{Narrative Roulette}, is both an engaging and effective learning environment for teenage students. But it won't be until teachers have the technical skills to deeply understand virtual microworlds, and authorities believe in constructionist learning, that microworlds will be adopted by the mainstream.
\end{abstract}

\tableofcontents

\chapter{Ideas}

\include{Background/1}
\include{Background/2}
\include{Background/3}
\include{Background/4}
\include{Background/5}

\chapter{Implementation}

\include{Project/6}
\include{Project/7}
\include{Project/8}

\chapter{Evaluation}

\include{Discussion/10}
\include{Discussion/11}
\include{Discussion/12}

\include{bibliography}

\end{document}
